---
title: "Homework 3"
author: "Mari Sanders"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(igraph)
library(tidyverse)
```

# Data 

```{r}
data <- read_delim("moreno_oz/out.moreno_oz_oz", skip = 1) %>% select(1:3) 
```

# Graphing Model 

This is a weighted graph, which contains friendship ratings between 217 residents living at a residence hall located on the Australian National University campus. 

Each node represents a person and each edge represents the friendship between the two nodes. 

```{r}
edge_list <- data %>% select(1:2) %>% as.data.frame()
g <- graph_from_data_frame(edge_list)
E(g)$weight <- data %>% select(3) %>% pull()
summary(g)
```

# Graphics 

```{r}
igraph_options(vertex.size=5, vertex.label=NA, edge.arrow.size=0.5)
plot(g, layout = layout_in_circle)
```

This type of graph does not seem to represent it well, as it is difficult to see all the edges in the graph. 

```{r}
igraph_options(vertex.size=5, vertex.label=NA, edge.arrow.size=0.5)
plot(g, layout = layout_with_fr)
```

This improved upon the circular graph, but it is still a bit difficult to see all the edges in the middle of the graph. It is easier to see the connections on the outside of the graph, but not the middle. 

```{r}
igraph_options(vertex.size=5, vertex.label=NA, edge.arrow.size=0.5)
plot(g, layout=layout_with_kk)
```

This is pretty similar to the above graph, where it is easy to see the connections on the outside, but not in the middle. 

```{r}
igraph_options(vertex.size=5, vertex.label=NA, edge.arrow.size=0.3)
plot(g, layout = layout_as_tree)
```

This actually isn't a terrible representation, but doesn't make sense for a traditional tree structure. Normally the direction of trees is only one way and this is not the case with the features of this graph. 
